---
title: "Womens Career Aspirations"
author: "Jeff Kennedy"
date: "23 November 2016"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 4, fig.height = 4)
```

```{r DataCleaning, echo = FALSE}
########################################################
#            Working Notes
#


# Drop out email addresses

# Consider reverse coded items - for calculating reliability
# the keys parameter can be used (psych package). If some
# of the items will be analysed on their own, may need to flag
# them in some way.
#
#
# D1_x vars have odd values (13, 14, etc). Need recoding.




# Get files into R
# Change path and file names as necessary.
folder <- file.path("C:","Users","jckenned","Documents","Consulting","Convergence Partners Survey","Data Analysis")
datafile1 <- "20161119_Womens_Careers_and_Aspirations.csv"
datafile2 <- "20161119_Womens_Careers_and_Aspirations_2.csv"
datafile3 <- "B4 and B5.csv"
library(dplyr)
library(readr) 
library(ggplot2)
library(psych)   # Creating scales and calculating reliability and other descriptives.
library(car)     # Used for the recode function.

# read_CSV in readr is better than R's built-in read.csv function; see Peng
# msdr.pdf p. 14.

# Nice info here on using the RStudio <Import Dataset> gui 
# for bringing in the csv file - creates syntax reflecting
# choices made. 
# https://support.rstudio.com/hc/en-us/articles/218611977-Importing-Data-with-RStudio

# Set up vector of variable names for use in the read_csv function.

varNames <- c("ResponseID", "ResponseSet", "Name", "ExtDataRef", "Email", 
              "IP_Add", "Status", "StartDate", "EndDate", "Finished", NA, 
              NA, NA, "Token", NA, "Marital", "Age", "WkHours", "JobStatus", 
              "JobStatTXT", "Deps0_5", "Deps5_10", "Deps11_18", "Deps19_30", 
              "DepsOther", NA, "JobTitle", "Seniority", "SeniorityTXT", 
              "Ethnic", "EthnicTXT", "Tenure", "Overseas", "Educ", "EducTXT", 
              "TotSal", "DirReps", "NinOrg", "OccGp", "Sector", "SectorTXT", 
              "NZRegion", "AKRegion", NA, "C1_1_ImpJob", "C1_2_ImpFam", 
              "C1_3_ImpLife", "C2_1_WLB", "C2_2_WLB", "C2_3_WLB", "C2_4_WLB", 
              "C2_5_WLB", "C3_Aspire", "C3_AspireTXT", "C4_AspChange", 
              "C4_AspChangeTXT", "C5_1_CarAdv", "C5_2_CarAdv", "C5_3_CarAdv", 
              "C5_4_CarAdv", "C5_5_CarAdv", "C5_6_CarAdv", "C5_7_CarAdv", 
              "C5_8_CarAdv", "C5_1_CarAdvTXT", "C6_PrimCareResp", 
              "C6_PrimCareRespTXT", "C7_PrimRespHHold", "C7_PrimRespHHoldTXT", 
              NA, "D1_1_Barrier", "D1_2_Barrier", "D1_5_Barrier", 
              "D1_6_Barrier", "D1_7_Barrier", "D1_7_BarrierTXT", "D1_8_Barrier",
              "D2_1_Conf", "D2_2_SE", "D2_3_PubSpk", "D2_4_IntPers", "D2_5_IQ", 
              "D2_6_PersEffic", "D2_7_PersEffect", "D2_8_Tech", "D3_1_Decn", 
              "D3_2_Grow", "D3_3_Probs", "D3_4_Chall", NA, "E1_1_CultFit", 
              "E1_2_CultFit", "E1_3_CultFit", "E1_4_CultFit", "E1_5_CultFit", 
              "E1_6_CultFit", "E1_7_CultFit", "E2_1_Network", "E2_2_Network", 
              "E3_1_Mentor", "E3_2_Mentor", "E3_3_Mentor", "E3_4_Mentor", 
              "E4_1_CarMgt", "E4_2_CarMgt", "E4_3_CarMgt", "E5_1_DevAsst", 
              "E5_2_DevAsst", "E5_3_DevAsst", "E5_4_DevAsst", "E5_5_DevAsst", 
              "E5_6_DevAsst", "E5_7_DevAsst", "E6_1_GeogMob", "E6_2_GeogMob", 
              "E6_3_GeogMob", "E6_4_GeogMob", "E6_5_GeogMob", "E6_6_GeogMob", 
              "E6_7_GeogMob", "E6_8_GeogMob", "E6_8_GeogMobTXT", "E7_Barriers", 
              NA, "F1_1_TrackRcd", "F2_1_OwnCareer", "F2_2_OwnCareer", 
              "F2_3_OwnCareer", "F2_4_OwnCareer", "F3_1_Relships", 
              "F3_2_Relships", "F3_3_Relships", "F3_4_Relships", "F4_1_Mentor", 
              "F4_2_Mentor", "F4_3_Mentor", "F4_4_Mentor", "F4_5_Mentor", 
              "F4_6_Mentor", "F4_7_Mentor", "F4_8_Mentor", "F5_1_DevAss", 
              "F5_2_DevAss", "F5_3_DevAss", "F5_4_DevAss", "F6_1_ProcJust", 
              "F6_2_ProcJust", "F6_3_ProcJust", "F6_4_ProcJust", 
              "F6_5_ProcJust", "F7_1_DistJust", "F7_2_DistJust", 
              "F7_3_DistJust", "F7_4_DistJust", "F7_5_DistJust", "F8_1_Empower",
              "F8_2_Empower", "F8_3_Empower", "F8_4_Empower", "F9_1_DevAss", 
              "F9_2_DevAss", "F9_3_DevAss", "F10_1_Turnover", "F10_2_Turnover", 
              "F10_3_Turnover", "F10_4_Turnover", "F11_1_JobSat", 
              "F11_2_JobSat", "F11_3_JobSat", "F11_4_JobSat", "F11_5_JobSat", 
              "F12_1_CareerSat", "F12_2_CareerSat", "F12_3_CareerSat", 
              "F12_4_CareerSat", "F12_5_CareerSat", "F13_1_LifeSat", 
              "F13_2_LifeSat", "F13_3_LifeSat", "F13_4_LifeSat", 
              "F13_5_LifeSat", NA, "F14a_1_CarSucc", "F14a_2_CarSucc", 
              "F14a_3_CarSucc", "F14b_CarSucc", "F14b_CarSuccTXT", NA, 
              "G1_AspST", "G2_AspLT", "G3_AspFactors", NA, NA, "H1_1_OrgFacil",
              "H1_2_OrgFacil", "H1_3_OrgFacil", "H1_4_OrgFacil", 
              "H1_5_OrgFacil", "H1_6_OrgFacil", "H1_7_OrgFacil", 
              "H1_8_OrgFacil", "H1_8_OrgFacilTXT", "H2_OrgDoMore", 
              "H3_OrgDoMoreTXT", "H4_1_Career_cfMen", "H4_2_Career_cfWom", 
              "H5_Recomm", "H6_RecommTXT", "H7_IncOrgPerf", "H8_IncOrgPerfTXT", 
              "H9_AddAnything", "H10_ParticInIv", "H11_GetCopy", "H12_Email", 
              NA, "Lat", "Long", "LocAcc", NA)


# I've specified column types for the Deps columns. Some people used 
# leading zeroes when entering number of dependents, and by default, 
# R treats these as characters. A leading zero in one datafile and not
# the other will result in different character formats, and the 
# bind function (for combining into one df) will fail.

data1 <- read_csv(file.path(folder, datafile1), 
         col_names = varNames,
         col_types = cols(StartDate = col_datetime(format = "%Y-%m-%d %H:%M:%S"), 
         EndDate = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
         Deps0_5 = col_integer(), Deps5_10 = col_integer(), 
         Deps11_18 = col_integer(), Deps19_30 = col_integer(), 
         DepsOther = col_integer()), 
         skip = 2)

data2 <- read_csv(file.path(folder, datafile2), 
         col_names = varNames,
         col_types = cols(StartDate = col_datetime(format = "%Y-%m-%d %H:%M:%S"), 
         EndDate = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
         Deps0_5 = col_integer(), Deps5_10 = col_integer(), 
         Deps11_18 = col_integer(), Deps19_30 = col_integer(), 
         DepsOther = col_integer()), 
         skip = 2)

data3 <- read_csv(file.path(folder, datafile3))
# data3 is the recoded B4 (Tenure) and B5 (Overseas) variables

# spec(data1) can be used to retrieve the class spec used on import.

# Now combine the datasets (.id parameter identifies which dataset each
# case comes from).

fulldata <- bind_rows(data1, data2, .id = "Source")

# identical(data3$ResponseID, fulldata$ResponseID) # Check that sets of 
# response IDs are same in data3 and fulldata.
fulldata <- full_join(fulldata, data3, by = "ResponseID")

# Used following when trying to find out which variables were 
# different classes in the two datasets. Equalitytest will have 
# FALSE for vars which differ.
#
# class1 <- sapply(data1, class)
# class2 <- sapply(data2, class)
# classasvector <- unlist(class1)
# classasvector2 <- unlist(class2)
# equalitytest <- classasvector == classasvector2

###### DATA CLEANING #######
# Select out D1_7, C5_8, E6_8, H1_8 (No info, relates to 'other' text comment)
# Select out all vars beginning with X (headings etc).
# Prob others can be dropped - ResponseSet etc.

responses <- fulldata %>% 
        select(-starts_with("X")) %>% 
        select(-ends_with("D1_7_Barrier")) %>% 
        select(-ends_with("C5_8_CarAdv")) %>% 
        select(-ends_with("E6_8_GeogMob")) %>% 
        select(-ends_with("H1_8_OrgFacil")) %>% 
        filter(ResponseID != "R_3GvvOBTj4XHfyeM") %>% 
        filter(ResponseID != "R_RKpGHXWPmVQx3Sp") %>% 
        filter(ResponseID != "R_2sbE1CxaFo6uCCG")
# Invalid responses dropped with filter

# Recode weird values in items - editing changes to Qualtrics survey
# means that some scales had gaps (e.g., 1-4, 6 instead of 1-5)
responses$C2_1_WLB <- car::recode(responses$C2_1_WLB,"13=1 ; 14=2 ; 15=3 ; 16=4 ; 17=5; else=NA")
responses$C2_2_WLB <- car::recode(responses$C2_2_WLB,"13=1 ; 14=2 ; 15=3 ; 16=4 ; 17=5; else=NA")
responses$C2_3_WLB <- car::recode(responses$C2_3_WLB,"13=1 ; 14=2 ; 15=3 ; 16=4 ; 17=5; else=NA")
responses$C2_4_WLB <- car::recode(responses$C2_4_WLB,"13=1 ; 14=2 ; 15=3 ; 16=4 ; 17=5; else=NA")
responses$C2_5_WLB <- car::recode(responses$C2_5_WLB,"13=1 ; 14=2 ; 15=3 ; 16=4 ; 17=5; else=NA")
responses$C3_Aspire <- car::recode(responses$C3_Aspire,"1=1 ; 2=2 ; 3=3 ; 4=4 ; 5=5 ; 6=6 ;
                                   8=7 ; 9=8 ; 7=9 ; 10=10 ; else=NA")
responses$C6_PrimCareResp <- car::recode(responses$C6_PrimCareResp, "1=1 ; 8=2 ; 9=3 ;10=4 ; 11=5 ; 12=6 ;
                                   13=7 ; 14=8 ; else=NA")
responses$D1_1_Barrier <- car::recode(responses$D1_1_Barrier,"13=1 ; 18=2 ; 14=3 ; 15=4 ; 16=5; else=NA")
responses$D1_2_Barrier <- car::recode(responses$D1_2_Barrier,"13=1 ; 18=2 ; 14=3 ; 15=4 ; 16=5; else=NA")
responses$D1_5_Barrier <- car::recode(responses$D1_5_Barrier,"13=1 ; 18=2 ; 14=3 ; 15=4 ; 16=5; else=NA")
responses$D1_6_Barrier <- car::recode(responses$D1_6_Barrier,"13=1 ; 18=2 ; 14=3 ; 15=4 ; 16=5; else=NA")
responses$D1_8_Barrier <- car::recode(responses$D1_8_Barrier,"13=1 ; 18=2 ; 14=3 ; 15=4 ; 16=5; else=NA")
responses$E4_1_CarMgt <- car::recode(responses$E4_1_CarMgt,"1=1 ; 2=2 ; 3=3 ; 4=4 ; 6=5; else=NA")
responses$E4_2_CarMgt <- car::recode(responses$E4_2_CarMgt,"1=1 ; 2=2 ; 3=3 ; 4=4 ; 6=5; else=NA")
responses$E4_3_CarMgt <- car::recode(responses$E4_3_CarMgt,"1=1 ; 2=2 ; 3=3 ; 4=4 ; 6=5; else=NA")
responses$F14a_1_CarSucc <- car::recode(responses$F14a_1_CarSucc,"1=1 ; 3=2 ; 4=3 ; 5=4 ; 6=5; 7=6; 8=7; else=NA")
responses$F14a_2_CarSucc <- car::recode(responses$F14a_2_CarSucc,"1=1 ; 3=2 ; 4=3 ; 5=4 ; 6=5; 7=6; 8=7; else=NA")
responses$F14a_3_CarSucc <- car::recode(responses$F14a_3_CarSucc,"1=1 ; 3=2 ; 4=3 ; 5=4 ; 6=5; 7=6; 8=7; else=NA")


#### Check missing responses in integer vars ###
numericvars <- responses[sapply(responses,is.numeric)]
# Sum number of missing responses in each row.
Missing <- apply(numericvars, 1, function(x) sum(is.na(x)))
allvars <- bind_cols(responses, as.data.frame(Missing))

# Create a numeric ID to help with creating scales later.
allvars$ID <- c(1:length(allvars$ResponseID))

# Note - bind_cols binds on position, not a key variable, but should
# be safe here.

# Following lines generate df containing only numeric varsfor Nazim; he
# uses PLS which doesn't like character variables:
WCA_Numeric <- allvars[sapply(allvars,is.numeric)]
write.csv(WCA_Numeric, file = "WCA_Numeric.csv")

# Following lines were to add Missing to numericvars for Nazim; he
# uses PLS which doesn't like character variables:
# WCA_Numeric <- bind_cols(numericvars, as.data.frame(Missing))
# write.csv(WCA_Numeric, file = "WCA_Numeric.csv")


```


```{r ScaleConstruction, echo = FALSE}
# Need to create scales for 5-pt and 7-pt scales separately or else
# recoding won't work.

keys.list_5 <- list(ID=c("ID"),
                  C2_WLB = c("-C2_1_WLB", "C2_2_WLB", "-C2_3_WLB", "-C2_4_WLB", 
                             "-C2_5_WLB"),
                  D1_PersCirc = c("D1_1_Barrier", "D1_2_Barrier", "D1_5_Barrier",
                                 "D1_6_Barrier", "D1_8_Barrier"),
                  D2_Abilities = c("D2_1_Conf", "D2_2_SE", "D2_3_PubSpk", 
                                   "D2_4_IntPers", "D2_5_IQ", "D2_6_PersEffic", 
                                   "D2_7_PersEffect", "D2_8_Tech"),
                  E1_CultFit = c("E1_1_CultFit", "E1_2_CultFit", "E1_3_CultFit",
                                 "E1_4_CultFit","E1_5_CultFit", "E1_6_CultFit",
                                 "E1_7_CultFit"),
                  E2_Network = c("E2_1_Network", "E2_2_Network"),
                  E3_Mentor = c("E3_1_Mentor", "E3_2_Mentor", "E3_3_Mentor",
                                "E3_4_Mentor"),
                  E4_CarMgt = c("E4_1_CarMgt", "E4_2_CarMgt", "E4_3_CarMgt"),
                  E5_DevAsst = c("E5_1_DevAsst", "E5_2_DevAsst", "E5_3_DevAsst",
                                 "E5_4_DevAsst", "E5_5_DevAsst", "E5_6_DevAsst",
                                 "E5_7_DevAsst"),
                  E6_GeoMob = c("E6_1_GeogMob", "E6_2_GeogMob", "E6_3_GeogMob"),
                  F2_MngCar = c("F2_1_OwnCareer", "F2_2_OwnCareer", 
                                "F2_3_OwnCareer", "F2_4_OwnCareer"),
                  F3_Relships = c("F3_1_Relships", "F3_2_Relships", 
                                  "F3_3_Relships", "F3_4_Relships"),
                  F4_Mentor = c("F4_1_Mentor", "F4_2_Mentor", "F4_3_Mentor", 
                                "F4_4_Mentor", "F4_5_Mentor", "F4_6_Mentor", 
                                "F4_7_Mentor", "F4_8_Mentor"),
                  F5_DevAss = c("F5_1_DevAss", "F5_2_DevAss", "F5_3_DevAss", 
                                "F5_4_DevAss"),
                  F6_ProcJust = c("F6_1_ProcJust", "-F6_2_ProcJust", 
                                  "-F6_3_ProcJust", "F6_4_ProcJust", 
                                  "F6_5_ProcJust"),
                  F7_DistJust = c("F7_1_DistJust", "F7_2_DistJust", "F7_3_DistJust", 
                                  "F7_4_DistJust", "F7_5_DistJust"),
                  F8_Empower = c("F8_1_Empower", "F8_2_Empower", "F8_3_Empower", 
                                 "F8_4_Empower"),
                  F9_DevAss = c("F9_1_DevAss", "F9_2_DevAss", "F9_3_DevAss"),
                  F10_Turnover = c("F10_1_Turnover", "F10_2_Turnover", 
                                   "F10_3_Turnover", "F10_4_Turnover"),
                  F11_JobSat = c("F11_1_JobSat", "F11_2_JobSat", "-F11_3_JobSat", 
                                 "F11_4_JobSat", "-F11_5_JobSat"),
                  F12_CareerSat =c("F12_1_CareerSat", "F12_2_CareerSat", 
                                   "F12_3_CareerSat", "F12_4_CareerSat", 
                                   "F12_5_CareerSat"),
                  F13_LifeSat = c("F13_1_LifeSat", "F13_2_LifeSat", "F13_3_LifeSat", 
                                  "F13_4_LifeSat", "F13_5_LifeSat"),
                  F14a_CarSucc = c("F14a_1_CarSucc", "F14a_2_CarSucc", "F14a_3_CarSucc"),
                  H1_OrgFacil =c("H1_1_OrgFacil", "H1_2_OrgFacil", "H1_3_OrgFacil", 
                                 "H1_4_OrgFacil", "H1_5_OrgFacil", "H1_6_OrgFacil", 
                                 "H1_7_OrgFacil")
                  )
itemsused_5 <- c("ID", "C2_1_WLB", "C2_2_WLB", "C2_3_WLB", "C2_4_WLB", "C2_5_WLB",
                 "D1_1_Barrier", "D1_2_Barrier", "D1_5_Barrier", 
                 "D1_6_Barrier", "D1_8_Barrier",
                 "D2_1_Conf", "D2_2_SE", "D2_3_PubSpk",
                 "D2_4_IntPers", "D2_5_IQ", "D2_6_PersEffic",
                 "D2_7_PersEffect", "D2_8_Tech",
                 "E1_1_CultFit", "E1_2_CultFit", "E1_3_CultFit", "E1_4_CultFit",
                 "E1_5_CultFit", "E1_6_CultFit", "E1_7_CultFit", "E2_1_Network", 
                 "E2_2_Network", "E3_1_Mentor", "E3_2_Mentor", "E3_3_Mentor", 
                 "E3_4_Mentor", "E4_1_CarMgt", "E4_2_CarMgt", "E4_3_CarMgt", 
                 "E5_1_DevAsst", "E5_2_DevAsst", "E5_3_DevAsst", "E5_4_DevAsst", 
                 "E5_5_DevAsst", "E5_6_DevAsst", "E5_7_DevAsst", 
                 "E6_1_GeogMob", "E6_2_GeogMob", "E6_3_GeogMob", 
                 "F2_1_OwnCareer", "F2_2_OwnCareer", "F2_3_OwnCareer", 
                 "F2_4_OwnCareer", "F3_1_Relships", "F3_2_Relships", 
                 "F3_3_Relships", "F3_4_Relships", "F4_1_Mentor", "F4_2_Mentor", 
                 "F4_3_Mentor", "F4_4_Mentor", "F4_5_Mentor", "F4_6_Mentor",
                 "F4_7_Mentor", "F4_8_Mentor", "F5_1_DevAss", "F5_2_DevAss", 
                 "F5_3_DevAss", "F5_4_DevAss", "F6_1_ProcJust", "F6_2_ProcJust", 
                 "F6_3_ProcJust", "F6_4_ProcJust", "F6_5_ProcJust", "F7_1_DistJust", 
                 "F7_2_DistJust", "F7_3_DistJust", "F7_4_DistJust", "F7_5_DistJust",
                 "F8_1_Empower", "F8_2_Empower", "F8_3_Empower", "F8_4_Empower",
                 "F9_1_DevAss", "F9_2_DevAss", "F9_3_DevAss",
                 "F10_1_Turnover", "F10_2_Turnover", "F10_3_Turnover", "F10_4_Turnover",
                 "F11_1_JobSat", "F11_2_JobSat", "F11_3_JobSat", "F11_4_JobSat", 
                 "F11_5_JobSat", "F12_1_CareerSat", "F12_2_CareerSat", 
                 "F12_3_CareerSat", "F12_4_CareerSat", "F12_5_CareerSat",
                 "F13_1_LifeSat", "F13_2_LifeSat", "F13_3_LifeSat", "F13_4_LifeSat", 
                 "F13_5_LifeSat", "F14a_1_CarSucc", "F14a_2_CarSucc", "F14a_3_CarSucc",
                 "H1_1_OrgFacil", "H1_2_OrgFacil", "H1_3_OrgFacil", "H1_4_OrgFacil", 
                 "H1_5_OrgFacil", "H1_6_OrgFacil", "H1_7_OrgFacil"
                 )
subset_allvars_5 <- allvars %>% dplyr::select(one_of(itemsused_5))
scores_5 <- scoreItems(keys.list_5, subset_allvars_5, impute="none", min=1, max=5, digits = 2)
# add the new scale scores to allvars using dplyr::left_join, matching by ID.
allvars <- dplyr::left_join(allvars, as.data.frame(scores_5$scores), by = "ID")

keys.list_7 <- list(ID=c("ID"), 
                    D3_CareerSE = c("D3_1_Decn", "D3_2_Grow", "D3_4_Chall"))
itemsused_7 <- c("ID", "D3_1_Decn", "D3_2_Grow", "D3_4_Chall")
subset_allvars_7 <- allvars %>% dplyr::select(one_of(itemsused_7))
scores_7 <- scoreItems(keys.list_7, subset_allvars_7, impute="none", min=1, max=5, digits = 2)
# add the new scale scores to allvars using dplyr::left_join, matching by ID.
allvars <- dplyr::left_join(allvars, as.data.frame(scores_7$scores), by = "ID")

############ Print off reliabilities etc. ####################
#
#      Can comment out this code when not required           #

# sink("Scale psychometrics.txt")
# scores_7$alpha
# scores_7$n.items
# scores_7$corrected
# scores_5$alpha
# scores_5$n.items
# scores_5$corrected
# sink()
```



```

## Missing data

Leaving aside optional questions (e.g., open text responses), this plot shows the number of missing values by respondent. Vertical axis is the number of respondents corresponding to each level of missing data along the horizontal axis.
```{r MissingValues, echo=FALSE}
ggplot(allvars, aes(Missing)) + geom_histogram(binwidth = 1)
```

## Importance of job, family, life/leisure

Total sample boxplots for Question C1:
C1 How would you rate the importance of the following to you?(0 - Not at all important; 100 - Extremely important)
1. ______ Career/ Job (1)
2. ______ Family/ Household (2)
3. ______ Lifestyle/ Leisure (e.g., sport, church) (3)

```{r C_1, echo=FALSE}
boxplot(allvars$C1_1_ImpJob,allvars$C1_2_ImpFam, allvars$C1_3_ImpLife, notch = TRUE, 
        names = c("Job", "Family", "Life"))
```

### Importance of job by demographics

Following boxplots show ratings of job importance according to marital status:  1. (Married/Partnered)
2. (Single)
3. (Other)

```{r, echo=FALSE}
ggplot(allvars, aes(Marital, C1_1_ImpJob)) + geom_boxplot(aes(group = factor(Marital)))
```

Following boxplots show ratings of job importance according to ethnicity:  
1. NZ European
2. Maori
3. Asian
4. Pacific peoples
5. Middle Eastern/ Latin American/African
6. Other


```{r, echo=FALSE}
ggplot(allvars, aes(Ethnic, C1_1_ImpJob)) + geom_boxplot(aes(group = factor(Ethnic)))
```

Following boxplots show ratings of job importance according to age group:  
1. 15--24
2. 25--34
3. 35--44
4. 45--54
5. 55--64
6. 65 & over


```{r, echo=FALSE}
ggplot(allvars, aes(Age, C1_1_ImpJob)) + geom_boxplot(aes(group = factor(Age)))
```

Following boxplots show ratings of job importance according to job status:  
1. Permanent
2. Temp/Short Contract
3. Self-employed
4. Other


```{r, echo=FALSE}
ggplot(allvars, aes(JobStatus, C1_1_ImpJob)) + geom_boxplot(aes(group = factor(JobStatus)))
```


### Importance of family by demographics

Following boxplots show ratings of family importance according to marital status:  1. (Married/Partnered)
2. (Single)
3. (Other)

```{r, echo=FALSE}
ggplot(allvars, aes(Marital, C1_2_ImpFam)) + geom_boxplot(aes(group = factor(Marital)))
```

Following boxplots show ratings of family importance according to ethnicity:  
1. NZ European
2. Maori
3. Asian
4. Pacific peoples
5. Middle Eastern/ Latin American/African
6. Other


```{r, echo=FALSE}
ggplot(allvars, aes(Ethnic, C1_2_ImpFam)) + geom_boxplot(aes(group = factor(Ethnic)))
```

Following boxplots show ratings of family importance according to age group:  
1. 15--24
2. 25--34
3. 35--44
4. 45--54
5. 55--64
6. 65 & over


```{r, echo=FALSE}
ggplot(allvars, aes(Age, C1_2_ImpFam)) + geom_boxplot(aes(group = factor(Age)))
```

Following boxplots show ratings of family importance according to job status:  
1. Permanent
2. Temp/Short Contract
3. Self-employed
4. Other


```{r, echo=FALSE}
ggplot(allvars, aes(JobStatus, C1_2_ImpFam)) + geom_boxplot(aes(group = factor(JobStatus)))
```

### Importance of life/leisure by demographics

Following boxplots show ratings of life/leisure importance according to marital status:  1. (Married/Partnered)
2. (Single)
3. (Other)

```{r, echo=FALSE}
ggplot(allvars, aes(Marital, C1_3_ImpLife)) + geom_boxplot(aes(group = factor(Marital)))
```

Following boxplots show ratings of life/leisure importance according to ethnicity:  
1. NZ European
2. Maori
3. Asian
4. Pacific peoples
5. Middle Eastern/ Latin American/African
6. Other


```{r, echo=FALSE}
ggplot(allvars, aes(Ethnic, C1_3_ImpLife)) + geom_boxplot(aes(group = factor(Ethnic)))
```

Following boxplots show ratings of life/leisure importance according to age group:  
1. 15--24
2. 25--34
3. 35--44
4. 45--54
5. 55--64
6. 65 & over


```{r, echo=FALSE}
ggplot(allvars, aes(Age, C1_3_ImpLife)) + geom_boxplot(aes(group = factor(Age)))
```

Following boxplots show ratings of life/leisure importance according to job status:  
1. Permanent
2. Temp/Short Contract
3. Self-employed
4. Other


```{r, echo=FALSE}
ggplot(allvars, aes(JobStatus, C1_3_ImpLife)) + geom_boxplot(aes(group = factor(JobStatus)))
```
